\documentclass[../chapter1/thesis_msc.tex]{subfiles}

\begin{document}
    \chapter*{Acknowledgments}
    \addcontentsline{toc}{chapter}{Acknowledgments}
    \phantomsection
    \thispagestyle{plain}

%    \paragraph{} Supervisors, advisor, fundi group, Busaba, Every friends who wear support me. 
\paragraph{} This thesis will never even started without this three gentleman, David Champion, Michael Kramer, and Norbert Langer. Especially David Champion with his endless enthusiasm to improve this work scientifically and grammatically. To be honest, I actually learn a lot under his supervision. I owe special thanks for Vishnu Balakrishnan and HTRU-S low lat collaboration for their endless night of observing for my data, Ewan Barr and Ralph Eatough for their long discussion about acceleration step in the FFA. I would like to thank Kira Kühn for her hard-working. I also would like to extend my gratitude to the Fundamental Physics in Radio Astronomy working group (alphabetically, forgive me if I missed anyone, I am writing this at 2 a.m.) Ioannis (John) Antoniadis, Rainer Beck, Xinping Deng, Gregory Desvignes, Paulo Freire, Eleni Graikou, Ramesh Karuppusamy,Hans-Rainer Klöckner, Marita Krause, Kuo Liu, Sui Ann Mao, Aristeidis Noutsos, Patricia Reich, Alessandro Ridolfi, Philip Schmidt, Laura Spitler, Caterina Tiburzi, ,Norbert Wex,Robert Wharton, Jason (Hung Kit) Wu, Olaf Wucknitz, Tilemachos Athanasiadis, Marina Berezina, Weiwei Chen, Marilyn Cruces, Madhuri Gaikwad, Tasha Gautam, Lorenz Haase, Guðjón Henning Hilmarsson, Leonard Houben, Maja Kierdorf, Yik Ki Ma, Jose Martinez,Nataliya Porayko, Christoph Schuermann,Prajwal Voraganti. 

\paragraph{} Since my English is pretty horrible, these people who are really outside pulsar science really helps me on giving opinions and correct my English, Pitshaporn, Atis, and Panas. Also, my best friend who swear since the first month that we met to change my English, Samuel Spencer. He even tried to correct my thesis on his birthday.    

\paragraph{} I would like to give my gratitude to Busaba Kramer for her helps, advice (and foods ?), without her help, I might not even survive in Germany. I also would like to say thank you to everyone that read my thesis. I hope that this thesis is not too hard to understand, trust me I tried my best already. 

\paragraph{} Lastly, I would like to say thank you to myself to survive throughout all of this work.
    \newpage
    \mbox{}
    \thispagestyle{empty}
\end{document}
